---
title: "Project Name"
author: "kattur"
date: ""
output: html_document

---

## Location of Phytophthora~host interactions

Here we provide tables showing the locations of Phytophthora~host interactions currently listed within our database, along with the pertitnent number of records.

If the combination of Phytopthora species and host has been recorded in Scotland, this is indicated as 'Yes' within the final column of the 'global' tables.

Separate sets of tables are provided for global (ex-UK) records, records from the UK (including Scotland), and records from Scotland only.

Combinations of Phytopthora species and host can be viewed at either host species or genus rank, by selecting the relevant option from the drop down menu on each tab.

Additionally, you can search by Phytopthora species or plant host name using the search box.

We have used the ______ as a standard _location information____ for the records within the database. 

The 'United Kingdom' is not a _____. Records relating to the United Kingdom may be ____ 'Ireland' (if Northern Ireland), or 'Great Britain' (if from England, Scotland, or Wales). Channel Island records _______. For this reason, the 'UK' tables display ________.


Where possible, locations have been allocated based on grid reference/lat long, where such information was not provided with a record, a match to WAGS has been attempted using a location name (e.g., state, province, country). ___ regions allocated on the basis of a name have the potential to have been mismatched to a ___, for example, if the the location of a record is given as the name of a country, but the location of the record is actually in an overseas territory of that country. However, the number of instances of such matches is considered as likely to be low.


There may be additional records within our database that relate to Phytopthora~host locations displayed in these tables, but either the location information has not yet been matched to a ____, or no location information is available for the record, and so it is not possible to include them here.




<br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = getwd())
library(DT)
library(raster)
library(knitr)
library(stringr)
library(dplyr)
library(kableExtra)
```
```{r host_data}


glob_species_1 <- read.csv("data/locat_glob_species_level_1.csv", stringsAsFactors = FALSE)

glob_species_2 <- read.csv("data/locat_glob_species_level_2.csv", stringsAsFactors = FALSE)

glob_species_3 <- read.csv("data/locat_glob_species_level_3.csv", stringsAsFactors = FALSE)

glob_species_4 <- read.csv("data/locat_glob_species_level_4.csv", stringsAsFactors = FALSE)

glob_genus_1 <- read.csv("data/locat_glob_genus_level_1.csv", stringsAsFactors = FALSE)

glob_genus_2 <- read.csv("data/locat_glob_genus_level_2.csv", stringsAsFactors = FALSE)

glob_genus_3 <- read.csv("data/locat_glob_genus_level_3.csv", stringsAsFactors = FALSE)

glob_genus_4 <- read.csv("data/locat_glob_genus_level_4.csv", stringsAsFactors = FALSE)

uk_species <- read.csv("data/locat_uk_species.csv", stringsAsFactors = FALSE)

uk_genus <- read.csv("data/locat_uk_genus.csv", stringsAsFactors = FALSE)

scot_species <- read.csv("data/locat_scot_species.csv", stringsAsFactors = FALSE)

scot_genus <- read.csv("data/locat_scot_genus.csv", stringsAsFactors = FALSE)

```

  

```{r}
library(DT)

glob_species_1_dt <- datatable(glob_species_1,
                             rownames = FALSE)

glob_species_2_dt <- datatable(glob_species_2,
                             rownames = FALSE)

glob_species_3_dt <- datatable(glob_species_3,
                             rownames = FALSE)

glob_species_4_dt <- datatable(glob_species_4,
                             rownames = FALSE)


glob_genus_1_dt <- datatable(glob_genus_1,
                             rownames = FALSE)

glob_genus_2_dt <- datatable(glob_genus_2,
                             rownames = FALSE)

glob_genus_3_dt <- datatable(glob_genus_3,
                             rownames = FALSE)

glob_genus_4_dt <- datatable(glob_genus_4,
                               rownames = FALSE)
                               

uk_species_dt <- datatable(uk_species,
                             rownames = FALSE)

uk_genus_dt <- datatable(uk_genus,
                             rownames = FALSE)


scot_species_dt <- datatable(scot_species,
                             rownames = FALSE)

scot_genus_dt <- datatable(scot_genus,
                             rownames = FALSE)

```

## {.tabset}

### Scotland{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
scot_species_dt   
```
#### Genus
```{r ,echo = FALSE}
scot_genus_dt
```
<!-- #### Family  -->
<!-- ```{r ,echo = FALSE} -->
<!-- scot_family_dt -->
<!-- ``` -->
##### {-}

### {-}


### UK{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
uk_species_dt   
```
#### Genus
```{r ,echo = FALSE}
uk_genus_dt
```
<!-- #### Family  -->
<!-- ```{r ,echo = FALSE} -->
<!-- uk_family_dt -->
<!-- ``` -->
##### {-}

### {-}

### Global Level 4{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
glob_species_4_dt   
```
#### Genus
```{r ,echo = FALSE}
glob_genus_4_dt
```
##### {-}

### {-}


### Global Level 3{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
glob_species_3_dt   
```
#### Genus
```{r ,echo = FALSE}
glob_genus_3_dt
```
##### {-}

### {-}


### Global Level 2{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
glob_species_2_dt   
```
#### Genus
```{r ,echo = FALSE}
glob_genus_2_dt
```
##### {-}

### {-}


### Global Level 1{.tabset .col-leftmid .tabset-dropdown}
#### Species 
```{r ,echo = FALSE}
glob_species_1_dt   
```
#### Genus
```{r ,echo = FALSE}
glob_genus_1_dt
```
##### {-}

### {-}


## {-}


Note:
  


<br>


